01_LH-SIP_Data_Reduction

### 2022-05-24 01_LH-SIP_Data_Reduction.Rmd
added .rds extensions

# Cache the sample files for plotting
saveRDS(sample_files, file = "cache/sample_files")

@@

```{r}
# Reduce the 0d --> 3d --> 7d incubation data
peaks_mapped_with_zeros_analytes_reduced <- peaks_mapped_with_zeros_analytes %>%
  # Add assimilation efficiency data
  mutate(
    a = d2H_assim_lm_summary$a_mn,
    sa = d2H_assim_lm_summary$sa
  ) %>% 
  # Column reduction
  select(Analysis,
         sample_id,
         terrain,
         soil,
         inc_time_d,
         inc_time_d_str,
         compound,
         area_FID,
         d2H_mn_zero,
         d2H,
         at2H_mn_zero,
         at2H_mn_zero_mc, # MC
         at2H, # not-corrected value
         calibrated_at2H_without_memory,
         calibrated_at2H_with_memory_correction, # MC
         area2_mn_zero,
         area2,
         area_FID,
         compound_ug_per_g_soil,
         a, # assimilation efficiency
         `2F_Me`,
         `2F_FAME`,
         `2F_FAME_mc`, # MC
         `2F_alk`,
         `2F_alk_mc`,  # MC
         F_label_mn,
         # Uncertainty terms:
         F_label_se, # error in the label strength (pipetting error)
         F_0_at2H_se, # error in the initial F_0 (instrument error)
         calibrated_at2H_without_memory_se, # error in F_T
         calibrated_at2H_with_memory_correction_se, # error in F_T, MC
         sa, # error in assimilation efficiency (se of literature values)
  ) %>% 
  # Turn all unit dbls into unitless
  mutate(
    across(
      where(is.numeric),
      as.numeric
    )
  )

@@

# Export
```{r}
# Export as RDS
saveRDS(peaks_mapped_with_zeros_analytes_reduced,
        file = "cache/LH_SIP_data")

saveRDS(peaks_mapped_with_threes_analytes_reduced,
        file = "cache/LH_SIP_data_3d_onwards")

saveRDS(F_L_2F,
        file = "cache/heavy_label_data")

saveRDS(d2H_assim_lm_summary,
        file = "cache/d2H_assimilation")

saveRDS(LH_SIP_memcorr,
        file = "cache/LH_SIP_memcorr")
```

>>>>

@@

```{r}
# Reduce the 0d --> 3d --> 7d incubation data
peaks_mapped_with_zeros_analytes_reduced <- peaks_mapped_with_zeros_analytes %>%
  # Add assimilation efficiency data
  mutate(
    a = d2H_assim_lm_summary$a_mn,
    sa = d2H_assim_lm_summary$sa
  ) %>% 
  # Column reduction
  select(Analysis,
         sample_id,
         terrain,
         soil,
         inc_time_d,
         inc_time_d_str,
         compound,
         area_FID,
         rel_area_FID,
         d2H_mn_zero,
         d2H,
         at2H_mn_zero,
         at2H_mn_zero_mc, # MC
         at2H, # not-corrected value
         calibrated_at2H_without_memory,
         calibrated_at2H_with_memory_correction, # MC
         area2,
         area_FID,
         compound_ug_per_g_soil,
         a, # assimilation efficiency
         `2F_Me`,
         `2F_FAME`,
         `2F_FAME_mc`, # MC
         `2F_alk`,
         `2F_alk_mc`,  # MC
         F_label_mn,
         # Uncertainty terms:
         F_label_se, # error in the label strength (pipetting error)
         F_0_at2H_se, # error in the initial F_0 (instrument error)
         calibrated_at2H_without_memory_se, # error in F_T
         calibrated_at2H_with_memory_correction_se, # error in F_T, MC
         sa, # error in assimilation efficiency (se of literature values)
  ) %>% 
  # Turn all unit dbls into unitless
  mutate(
    across(
      where(is.numeric),
      as.numeric
    )
  )

@@

# Export
```{r}
# Export as RDS
saveRDS(peaks_mapped_with_zeros_analytes_reduced,
        file = "cache/LH_SIP_data.RDS")

saveRDS(peaks_mapped_with_threes_analytes_reduced,
        file = "cache/LH_SIP_data_3d_onwards.RDS")

saveRDS(F_L_2F,
        file = "cache/heavy_label_data.RDS")

saveRDS(d2H_assim_lm_summary,
        file = "cache/d2H_assimilation.RDS")

saveRDS(LH_SIP_memcorr,
        file = "cache/LH_SIP_memcorr.RDS")

saveRDS(sample_files, 
        file = "cache/sample_files.RDS")
```
